Effects of Antenna Beam Chromaticity on Redshifted 21~cm Power Spectrum and Implications for Hydrogen Epoch of Reionization Array

### 2016-03-26 ForegroundSimulations/ms.tex
Incorporate Judd's suggestions in Abstract
From 4b3c3b1 (fgsim):
====================

In ms.tex,

(*) Incorporate Judd's suggestions in Abstract

Unaccounted systematics from foregrounds and instruments limit sensitivity of current experiments from detecting redshifted 21~cm signal from the Epoch of Reionization (EoR). Upcoming experiments are faced with a challenge to deliver more collecting area per antenna element without degrading the data with systematics. This paper and its companions show that dishes are viable for achieving this balance using the Hydrogen Epoch of Reionization Array (HERA) as an example. In this paper, we specifically identify spectral systematics associated with the antenna power pattern as a significant detriment affecting all EoR experiments. Chromaticity of the antenna beam causes the already bright foreground power to leak well beyond ideal limits and contaminate the otherwise clean EoR signal modes. A primary source of this chromaticity is reflections in the antenna-feed assembly and between structures in neighboring antennas. Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated design specifications on these reflections to prevent further EoR signal degradation and show HERA will not be impeded by such spectral systematics. Using a simple and yet high dynamic range spectral weighting scheme, we demonstrate that even in a conservative scenario that does not perform removal of foregrounds, HERA will detect EoR signal in line-of-sight $k$-modes, $k_\parallel \gtrsim 0.2\,h$~Mpc$^{-1}$, with high significance. All baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.

@@

\citet{deb16} describe the instrument in detail while \citet{pob14} explored the range of astrophysical parameters that can be probed with HERA. We provide a summary of the instrument currently under construction on the South African SKA site.

@@

We assume the interpretation that reflections cause additional spectral structures in the antenna power pattern in which they would be absent otherwise. Thus, we use an antenna power pattern in which those spectral structures from reflections which we are interested in addressing are absent but the intrinsic chromaticity of foregrounds and the geometric phases of baselines are included. $\Gamma_{k_\textrm{p}}(\tau)$ is determined by the requirement that the reflected foreground power so obtained, after shifting in delay, lies below the EoR H{\sc i} signal power in line-of-sight spatial scales of interest, $|k_\parallel|>k_\textrm{p}$. Thus, by disentangling spectral systematics inherent in the antenna power pattern from the overall EoR-foreground dynamic range, a design requirement that sets a limit on that systematic is obtained.

@@

Similarly, for reflections arising out of structures and interfaces across different antennas, we use $P_\textrm{FG}(k_\parallel)$ obtained with the simulated chromatic and {\it Airy} antenna beams on 14.6~m baselines. The simulated chromatic pattern in fact includes explicit simulations of reflections between structures within an antenna subsystem while the {\it Airy} pattern is assumed to include these effects. But both these beams do not include spectral features from antenna-to-antenna reflections. Thus $\Gamma_{k_\textrm{p}}(\tau)$ provides lower limit for attenuation of such antenna-to-antenna reflections. Fig.~\ref{fig:fg-reflections} is similar to Fig.~\ref{fig:fg-reflections-achrmbeam} with constraints for values of $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (left), 0.15~$h$~Mpc$^{-1}$ (middle), and 0.2~$h$~Mpc$^{-1}$ (right). Lower limits are estimated for {\it Airy} (dashed lines) and simulated chromatic beams (solid lines).

>>>>

Unaccounted for systematics from foregrounds and instruments limit the sensitivity of current experiments from detecting redshifted 21~cm signals from the Epoch of Reionization (EoR). Upcoming experiments are faced with a challenge to deliver more collecting area per antenna element without degrading the data with systematics. This paper and its companions show that dishes are viable for achieving this balance using the Hydrogen Epoch of Reionization Array (HERA) as an example. Here, we specifically identify spectral systematics associated with the antenna power pattern as a significant detriment to all EoR experiments which causes the already bright foreground power to leak well beyond ideal limits and contaminate the otherwise clean EoR signal modes. A primary source of this chromaticity is reflections in the antenna-feed assembly and between structures in neighboring antennas. Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated design specifications on these reflections to prevent further EoR signal degradation. We show HERA will not be impeded by such spectral systematics and demonstrate that even in a conservative scenario that does not perform removal of foregrounds, HERA will detect EoR signal in line-of-sight $k$-modes, $k_\parallel \gtrsim 0.2\,h$~Mpc$^{-1}$, with high significance. All baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.

@@

\citet{deb16} describe the HERA instrument in detail while \citet{pob14} explored the range of astrophysical parameters that HERA can probe. We provide a summary of the instrument currently under construction on the South African SKA site.

@@

We adopt the interpretation that reflections cause additional spectral structures in the antenna power pattern in which they would be absent otherwise. Thus, we use an antenna power pattern in which those spectral structures from reflections which we are interested in addressing are absent but the intrinsic chromaticity of foregrounds and the geometric phases of baselines are included. $\Gamma_{k_\textrm{p}}(\tau)$ is determined by the requirement that the reflected foreground power so obtained, after shifting in delay, lies below the EoR H{\sc i} signal power in line-of-sight spatial scales of interest, $|k_\parallel|>k_\textrm{p}$. Thus, by disentangling spectral systematics inherent in the antenna power pattern from the overall EoR-foreground dynamic range, a design requirement that sets a limit on that systematic is obtained.

@@

Similarly, for reflections arising out of structures and interfaces across different antennas, we use $P_\textrm{FG}(k_\parallel)$ obtained with the simulated chromatic and {\it Airy} antenna beams on 14.6~m baselines. The simulated chromatic pattern in fact includes explicit simulations of reflections between structures within an antenna subsystem. We assume the same is true for the {\it Airy} pattern as well. But both these beams do not include spectral features from antenna-to-antenna reflections. Thus $\Gamma_{k_\textrm{p}}(\tau)$ provides lower limit for attenuation of such antenna-to-antenna reflections. Fig.~\ref{fig:fg-reflections} is similar to Fig.~\ref{fig:fg-reflections-achrmbeam} with constraints for values of $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (left), 0.15~$h$~Mpc$^{-1}$ (middle), and 0.2~$h$~Mpc$^{-1}$ (right). Lower limits are estimated for {\it Airy} (dashed lines) and simulated chromatic beams (solid lines).
